%====================================================================================================
\begin{abstractpage}{Acknowledgments}
%====================================================================================================
I would like to express my profound sincere gratitude to Prof. Junpei Maeda and Prof. Yuji Yamazaki, who have continuously guided and supported my research throughout my master’s program. Their patience, encouragement, and insightful advice were crucail in the completing this thesis. Prof. Junpei Maeda provided continuous technical guidance and encouragement during the most challenging phases of my work. Prof. Yuji Yamazaki, as my supervisor, guided the overall direction of my study and provided detailed feedback and on this thesis. Without their support, the completion of this thesis would have been impossible.

I would like to thank Prof. Hisaya Kurashige from Kobe ATLAS group for his guidance during weekly meetings and for his kind assistance in discussions related to physics. I would also like to express my gratitude to other teachers in our research room: Prof. Yasuo Takeuchi, Prof. Kentaro Miuchi, Prof. Hiroshi Ito, Satoshi Higashino, for their assistance during my presentations and colloquiums.

I am grateful to Prof. Susumu Okubo and Prof. Junpei Maeda for taking the time to review my thesis as secondary examiners, despite their busy schedules.

I would like to extend my appreciation to the former members of Kobe ATLAS group during my master’s studies: Koya Toji, Yui Murata, Ryugo Mizuhiki, Rukumo Higuchi, Shota Nishi, as well as the current members: Ryosuke Tanaka, Rintaro Yamaguchi, Yuma Sano, Yuki Asami, Keita Sakura, and Masahiro Sasada, for their company and help throughout my master’s research journey.

I would also like to acknowledge the contributions of members of ATLAS Japan group in ICEPP: Erika Yamashita, Airu Makita, Towa Mizuochi, and Kazuma Maki, who provided valuable advice and continuously shared their research progress related to my study, which was beneficial for my own research.

Finally, I would like to express my deepest gratitude to my parents, who have always supported and encouraged me unconditionally. They provided me with the opportunity to experience studying and communicating overseas. I offer them my highest respect and heartfelt thanks.

\par\bigskip
\par\bigskip

\begin{flushright}
\par\bigskip
\textbf{Li Zhang}\\
\textbf{Kobe, the 8th of August 2025}
\end{flushright}
%====================================================================================================
\end{abstractpage}
%====================================================================================================
